Figures for "Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)

### 2022-05-03 report.Rmd
update figs
update ld_disc

```{r}
targets::tar_load("fit_sp_0_summary_simple")
targets::tar_load("fit_sp_1_summary_model")
targets::tar_load("fit_sp_2_summary_model")
targets::tar_load("fit_sp_3_summary_model")
targets::tar_load("fit_sp_4_summary_sma")
targets::tar_load("fit_sp_5_summary_sma")
targets::tar_load("fit_sp_6_summary_sma_err")

targets::tar_load("fit_sp_0_diagnostics_simple")
targets::tar_load("fit_sp_1_diagnostics_model")
targets::tar_load("fit_sp_2_diagnostics_model")
targets::tar_load("fit_sp_3_diagnostics_model")
targets::tar_load("fit_sp_4_diagnostics_sma")
targets::tar_load("fit_sp_5_diagnostics_sma")
targets::tar_load("fit_sp_6_diagnostics_sma_err")
```

```{r}
fit_sp_0_summary_simple |> filter(rhat > 1.1)
fit_sp_1_summary_model |> filter(rhat > 1.1)
fit_sp_2_summary_model |> filter(rhat > 1.1)
fit_sp_3_summary_model |> filter(rhat > 1.1)
fit_sp_4_summary_sma |> filter(rhat > 1.1)
fit_sp_5_summary_sma |> filter(rhat > 1.1)
fit_sp_6_summary_sma_err |> filter(rhat > 1.1)
```

@@

```{r}
div_check(fit_sp_0_diagnostics_simple)
div_check(fit_sp_1_diagnostics_model)
div_check(fit_sp_2_diagnostics_model)
div_check(fit_sp_3_diagnostics_model)
div_check(fit_sp_4_diagnostics_sma)
div_check(fit_sp_5_diagnostics_sma)
div_check(fit_sp_6_diagnostics_sma_err)
```

```{r}
targets::tar_load(loo_model)
loo::loo_compare(loo_model[[1]], loo_model[[2]], loo_model[[3]], loo_model[[4]])
```

@@

@@

>>>>

```{r}
targets::tar_load("fit_sp_0_summary_simple")
targets::tar_load("fit_sp_1_summary_model")
targets::tar_load("fit_sp_11_summary_model")
targets::tar_load("fit_sp_2_summary_model")
targets::tar_load("fit_sp_21_summary_model2")
targets::tar_load("fit_sp_3_summary_model")
targets::tar_load("fit_sp_31_summary_model")
targets::tar_load("fit_sp_32_summary_model")
# targets::tar_load("fit_sp_4_summary_sma")
# targets::tar_load("fit_sp_5_summary_sma")
# targets::tar_load("fit_sp_6_summary_sma_err")

targets::tar_load("fit_sp_0_diagnostics_simple")
targets::tar_load("fit_sp_1_diagnostics_model")
targets::tar_load("fit_sp_11_diagnostics_model")
targets::tar_load("fit_sp_2_diagnostics_model")
targets::tar_load("fit_sp_21_diagnostics_model2")
targets::tar_load("fit_sp_3_diagnostics_model")
targets::tar_load("fit_sp_31_diagnostics_model")
targets::tar_load("fit_sp_32_diagnostics_model")
# targets::tar_load("fit_sp_4_diagnostics_sma")
# targets::tar_load("fit_sp_5_diagnostics_sma")
# targets::tar_load("fit_sp_6_diagnostics_sma_err")
```

```{r}
fit_sp_0_summary_simple |> filter(rhat > 1.1)
fit_sp_1_summary_model |> filter(rhat > 1.1)
fit_sp_11_summary_model |> filter(rhat > 1.1)
fit_sp_2_summary_model |> filter(rhat > 1.1)
fit_sp_21_summary_model2 |> filter(rhat > 1.1)
fit_sp_3_summary_model |> filter(rhat > 1.1)
fit_sp_31_summary_model |> filter(rhat > 1.1)
fit_sp_32_summary_model |> filter(rhat > 1.1)
# fit_sp_4_summary_sma |> filter(rhat > 1.1)
# fit_sp_5_summary_sma |> filter(rhat > 1.1)
# fit_sp_6_summary_sma_err |> filter(rhat > 1.1)
```

@@

```{r}
div_check(fit_sp_0_diagnostics_simple)
div_check(fit_sp_1_diagnostics_model)
div_check(fit_sp_11_diagnostics_model)
div_check(fit_sp_2_diagnostics_model)
div_check(fit_sp_21_diagnostics_model2)
div_check(fit_sp_3_diagnostics_model)
div_check(fit_sp_31_diagnostics_model)
div_check(fit_sp_32_diagnostics_model)
# div_check(fit_sp_4_diagnostics_sma)
# div_check(fit_sp_5_diagnostics_sma)
# div_check(fit_sp_6_diagnostics_sma_err)
```

```{r}
targets::tar_load(loo_model)
loo::loo_compare(loo_model[[1]], loo_model[[2]], loo_model[[3]],
  loo_model[[4]], loo_model[[5]], loo_model[[6]], loo_model[[7]], loo_model[[8]])
```

@@

```{r, eval=TRUE}
tar_load(coef_sp_png1)
```

![](figs/coef_sp1.png)

@@

```{r, eval=TRUE}
tar_load(coef_sp_png31)
```

![](figs/coef_sp31.png)

```{r, eval=TRUE}
tar_load(coef_sp_png333)
```

![](figs/coef_sp333.png)
